\textbf{ Joystream: A Protocol for User Governed Content Platforms }

### 2019-02-25 paper.tex
CID -> Authority Key wrt verification
Clarify wording: downloaders and distributors are both members

\item
The distributor sends verifiable (based on CID) data chunks, in response to requests from the downloader, in a tit-for-tat exchange. The member sends a signature over the claim that a certain total amount of data has been transmitted over the lifetime of the session, analogous to payment channels \cite{payment_channels}. To avoid latency there should be some amount of pipelinining.

>>>>

\item
The distributor sends verifiable (based on Authority Key) data chunks, in response to requests from the downloader, in a tit-for-tat exchange. The downloader sends to the distributor a signature over the claim that a certain total amount of data has been transmitted over the lifetime of the session, analogous to payment channels \cite{payment_channels}. To avoid latency there should be some amount of pipelinining.
